# MLR With Pre-Learning Concentrations {.panelset}

* Response Variable: PavCA
* Predictors: Pre-learning concentrations of analytes
* Covariate: Sex

```{r}
pre.data <- all.data %>%
  select(PavCA, Sex, ends_with("Pre")) %>%
  drop_na()
```


## Full Model

### Model Fitting
```{r}
pre.full <- mod.runner(pre.data)
pre.cv <- cv.lm(pre.data)
```

* **$R^2$**: `r paste0(round(100*pre.full$R2, 2), "%")`
* **RMSE**: `r round(pre.full$rmse, 4)`, **Cross-Validated RMSE**: `r round(pre.cv$cv.rmse, 4)`
* **NRMSE**: `r paste0(round(pre.full$nrmse, 2), "%")`, **Cross-Validated NRMSE**: `r paste0(round(pre.cv$cv.nrmse, 2), "%")`
* **Significant Predictors**: `r paste0(pre.full$signif05, collapse = ", ")`
* **Phenotype Prediction Accuracy**: 
```{r} 
nice_table(data.frame(
  "Cutoff" = c(0.3, 0.4, 0.5),
  "Accuracy" = paste0(c(
    round(pre.full$Phenotype3.accu, 2),
    round(pre.full$Phenotype4.accu, 2),
    round(pre.full$Phenotype5.accu, 2)
  ), "%"),
  "CV Accuracy" = paste0(c(
    round(pre.cv$cv.P3.acc, 2),
    round(pre.cv$cv.P4.acc, 2),
    round(pre.cv$cv.P5.acc, 2)
  ), "%")
  ))
```

### Model Diagnostics
* *Checking Multicollinearity*
```{r pre-coll, message = FALSE, warning = FALSE, out.width='80%', fig.asp=.75, fig.align='center'}
pre.full$check_collinearity

```

* *Other Diagnostics*
```{r pre-diag, message = FALSE, warning = FALSE, out.width='80%', fig.asp=.75, fig.align='center'}
pre.full$check_model
```
* *Influential Points*: `r paste0(pre.full$influential, collapse = ", ")`













