# MLR With Post-Learning Concentrations {.panelset}

* Response Variable: PavCA
* Postdictors: Post-learning concentrations of analytes
* Covariate: Sex

```{r}
post.data <- all.data %>%
  select(PavCA, Sex, ends_with("Post")) %>%
  drop_na()
```


## Full Model

### Model Fitting
```{r}
post.full <- mod.runner(post.data)
post.full.cv <- cv.lm(post.data)
```

* **$R^2$**: `r paste0(round(100*post.full$R2, 2), "%")`
* **RMSE**: `r round(post.full$rmse, 4)`, **Cross-Validated RMSE**: `r round(post.full.cv$cv.rmse, 4)`
* **NRMSE**: `r paste0(round(post.full$nrmse, 2), "%")`, **Cross-Validated NRMSE**: `r paste0(round(post.full.cv$cv.nrmse, 2), "%")`
* **Significant Postdictors**: `r paste0(post.full$signif05, collapse = ", ")`
* **Phenotype Postdiction Accuracy**: 
```{r} 
nice_table(data.frame(
  "Cutoff" = c(0.3, 0.4, 0.5),
  "Accuracy" = paste0(c(
    round(post.full$Phenotype3.accu, 2),
    round(post.full$Phenotype4.accu, 2),
    round(post.full$Phenotype5.accu, 2)
  ), "%"),
  "CV Accuracy" = paste0(c(
    round(post.full.cv$cv.P3.acc, 2),
    round(post.full.cv$cv.P4.acc, 2),
    round(post.full.cv$cv.P5.acc, 2)
  ), "%")
  ))
```

### Model Diagnostics
* *Checking Multicollinearity*
```{r post-coll, message = FALSE, warning = FALSE, out.width='80%', fig.asp=.75, fig.align='center'}
post.full$check_collinearity

```

* *Other Diagnostics*
```{r post-diag, message = FALSE, warning = FALSE, out.width='80%', fig.asp=.75, fig.align='center'}
post.full$check_model
```
* *Influential Points*: `r paste0(post.full$influential, collapse = ", ")`

## AIC Model
### Stepwise Selection Using AIC
* Selected postdictors
```{r}
post.step <- step(lm(PavCA ~ ., data = post.data), direction = "both", k = 2,
                  trace = F)
paste0(names(coef(post.step))[-1], collapse = ", ")

post.aic.data <- post.data %>%
  select(PavCA, Sex, all_of(names(coef(post.step))[-(1:2)]))
```

### Model Fitting
```{r}
post.aic <- mod.runner(post.aic.data)
post.aic.cv <- cv.lm(post.aic.data)
```

* **$R^2$**: `r paste0(round(100*post.aic$R2, 2), "%")`
* **RMSE**: `r round(post.aic$rmse, 4)`, **Cross-Validated RMSE**: `r round(post.aic.cv$cv.rmse, 4)`
* **NRMSE**: `r paste0(round(post.aic$nrmse, 2), "%")`, **Cross-Validated NRMSE**: `r paste0(round(post.aic.cv$cv.nrmse, 2), "%")`
* **Significant Postdictors**: `r paste0(post.aic$signif05, collapse = ", ")`
* **Phenotype Postdiction Accuracy**: 
```{r} 
nice_table(data.frame(
  "Cutoff" = c(0.3, 0.4, 0.5),
  "Accuracy" = paste0(c(
    round(post.aic$Phenotype3.accu, 2),
    round(post.aic$Phenotype4.accu, 2),
    round(post.aic$Phenotype5.accu, 2)
  ), "%"),
  "CV Accuracy" = paste0(c(
    round(post.aic.cv$cv.P3.acc, 2),
    round(post.aic.cv$cv.P4.acc, 2),
    round(post.aic.cv$cv.P5.acc, 2)
  ), "%")
  ))
```
